\textcolor{Navy}{\textsc{Convexity adjustments with a bit of Malliavin}}

### 2022-09-15 Latex/paper.tex
# convexity adjustment for fra in arrears

\hspace{1cm}
\fboxsep1em
\fbox{\parbox{435pt}
{
\begin{equation}\label{ca_approximation_futures}
CA(t,t_0,t_1) \approx \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2) \frac{P_{ois}(0,t_2)}{P_{ois}(0,t_0)} - G(t_0,t_1) \frac{P_{ois}(0,t_1)}{P_{ois}(0,t_0)}\right) \int_{0}^{t_0}  \beta(s,t_0, x_0, \hat{y}_s) \nu(s,t_2) ds. 
\end{equation}
}}
\begin{example}\label{example_ca_future}
Let us to set 
\begin{align*}
g(T) &= \exp(-kT) \\
h(t) &= \sigma
\end{align*}
\end{example}
With this parametrization, the Cheyette model is equiavalent to Hull-White model. It is easy to show that under this parametrization, the convexity adjustment (\ref{ca_approximation_futures}) is
\begin{align*}
CA(t,t_0,t_1) & \approx \frac{\sigma^{2} \exp(-k t_0)  P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(\frac{1 - \exp(- k t_0)}{k^{2}} - \frac{t_0 \exp(-k t_2)}{k} \right).   
\end{align*}
In the next figure, we can check the accuracy of the last formula versus montecarlo. The parameters that we have used are $\sigma=0.05$, $k=0.003$ and flat curve with level $r=0.01$.

@@

@@

\subsection{FRAs in arrears}

>>>>

\hspace{1cm}
\fboxsep1em
\fbox{\parbox{435pt}
{
\begin{equation}\label{ca_approximation_futures}
CA(t,t_0,t_1) \approx \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2) \frac{P_{ois}(0,t_2)}{P_{ois}(0,t_0)} - G(t_0,t_1) \frac{P_{ois}(0,t_1)}{P_{ois}(0,t_0)}\right) \int_{0}^{t_0}  \beta(s,t_0, x_0, \hat{y}_s) \nu(s,t_2) ds. 
\end{equation}
}}
\begin{example}\label{example_ca_future}
Let us to set 
\begin{align*}
g(T) &= \exp(-kT) \\
h(t) &= \sigma
\end{align*}
\end{example}
With this parametrization, the Cheyette model is equiavalent to Hull-White model. It is easy to show that under this parametrization, the convexity adjustment (\ref{ca_approximation_futures}) is
\begin{align*}
CA(t_0,t_1) & \approx \frac{\sigma^{2} \exp(-k t_0)  P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(\frac{1 - \exp(- k t_0)}{k^{2}} - \frac{t_0 \exp(-k t_2)}{k} \right).   
\end{align*}
In the next figure, we can check the accuracy of the last formula versus montecarlo. The parameters that we have used are $\sigma=0.05$, $k=0.003$ and flat curve with level $r=0.01$.

@@

\newpage

@@

\subsection{FRAs in arrears}
The cash flows associated to a FRAs in arrears is $L_{E}(t_1,t_1,t_2)$ in $t_1$. Therefore the payment will be
\begin{equation}
P_{E}(0,t_1)\mathbb{E}^{\mathbb{Q}^{t_1}}\left( L_{E}(t_1,t_1,t_2\right).
\end{equation}
The expected value is clearly taken with respect to the wrong martingale, because $L_{E}(t,t_1,t_2)$ is martingale under the measure $\mathbb{Q}^{t_2}$. In order to calculate, the convexity adjustment we will use as before Clark-Ocone to get a representation for $L_{E}(t_1,t_1,t_2)$ i.e
\begin{equation}\label{general_convexity_fras}
L_{E}(t_1,t_1,t_2) = \mathbb{E}^{\mathbb{Q}^{t_2}}\left(L_{E}(t_1,t_1,t_2) \right) + \int_{0}^{t_1} \mathbb{E}^{\mathbb{Q}^{t_2}}\left(D_s L_{E}(t_1,t_1,t_2) \right) dW^{\mathbb{Q}^{t_2}}_{s}
\end{equation}
The if we suppose the HJM dynamic (\ref{estimation_forward_rate_curve})and we take $\mathbb{E}^{^{\mathbb{Q}^{t_1}}}(\cdot)$ we get
\begin{align*}
\mathbb{E}^{\mathbb{Q}^{t_1}}\left(L_{E}(t_1,t_1,t_2) \right) &= L_{E}(0,t_1,t_2) + \mathbb{E}\left( \int_{0}^{t_1} \mathbb{E}^{\mathbb{Q}^{t_2}}\left(D_s L_{E}(t_1,t_1,t_2) \right) dW^{\mathbb{Q}^{t_2}}_{s}\right)\\
&= L_{E}(0,t_1,t_2) + \mathbb{E}\left( \int_{0}^{t_1} \mathbb{E}^{\mathbb{Q}^{t_2}}\left(D_s L_{E}(t_1,t_1,t_2) \right) (\nu(s,t_2)-\nu(s,t_1)) ds \right)
\end{align*}
Where we have used that 
\begin{equation*}
dW^{\mathbb{Q}^{t_2}}_s = dW^{\mathbb{Q}^{t_1}}_s + (\nu(s,t_2) - \nu(s,t_1)) ds 
\end{equation*}
Now from (\ref{malliavin_derive_x}) we have that 
\begin{equation*}
D_s L(t_1,t_1,t_2) = \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(t_1,t_2)} D_s x_{t_1} \approx \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \beta(s,t_1, x_0, \hat{y}_s)M(s,t_1)
\end{equation*}
Therefore, if we define 
\begin{equation*}
CA(t_0,t_1) = \mathbb{E}^{\mathbb{Q}^{t_1}}\left( L_{E}\left(t_1,t_1,t_2\right)\right) - L_{E}\left(0,t_1,t_2\right)
\end{equation*}
and we use the last approximation and (\ref{general_convexity_fras}), we can get the next approximation for $CA(t_0,t_1)$ 
\hspace{2cm}
\fboxsep1em
\fbox{\parbox{435pt}
{
\begin{equation}\label{ca_approximations_fra_arrears}
CA(t_0,t_1) \approx  \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \int_{0}^{t_1} \beta(s,t_1, x_0, \hat{y}_s) (\nu(s,t_2) - \nu(s,t_1)) ds.
\end{equation}
}}
\begin{example}
To check how works the last approximation. We will restrict a Hull-White model with mean reversion and volatility constant. We will use are $\sigma=0.1$, $k=0.007$ for our model. The analytical approximation that we get from (\ref{ca_approximation_futures}) is
\begin{equation*}
CA(t_0,t_1) \approx \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)}  \frac{\sigma^{2}}{k} \int_{0}^{t_1} \exp(- k(t_1 + u)) -   \exp(- k(t_2 + u)) du 
\end{equation*}
We have checked the last approximation using MC method to compute the value of a FRA in arrears. We will show the result of the simulation in the next figure

\begin{figure}[h]
	\begin{center}
		\includegraphics[scale=0.3]{Figures/fra_convexity.jpg}
		\caption{Convexity Mc Vs Convexity Malliavin}
	\end{center}
\end{figure}

\end{example}

\newpage
